Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus

### 2023-11-15 manuscript_thev_transcriptome.Rmd
made publication-worthy figures and removed uneeded figs

**Changes in THEV splicing profile over time**   
AdV gene expression occurs under exquisite temporal control, supervised by designated promoters for each transcription unit (TU). Each promoter typically produce one or few pre-mRNAs that undergo alternative splicing to yield the manifold repertoire of complex transcripts characteristic of AdVs. To evaluate the activity of each promoter over time, Firstly, `Ballgown` - a program for statistical analysis of assembled transcriptomes, was used to estimate and normalize expression levels of all transcripts in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units over time. Very few unique splice junctions, reads, and transcripts were counted at 4 h.p.i; hence, this time point was excluded in this analysis.This analysis revealed DBP - from the E2 region - to be the most significantly expressed at 12 h.p.i, whereas MLP region transcripts were most abundantly expressed at 24 and 72 h.p.i as expected (__Figure 4a__). Also, our analysis of the FPKM values of transcripts by region showed a similar pattern: the E2 region as the most significantly overexpressed at 12 h.p.i, after which the MLP region assumes predominance (__Figure 4b__).  
Secondly, we estimated relative abundances of all splice junctions for each time point, counting as significantly expressed only those with coverage of at least 1% of the total splice junction reads counted at the given time point. At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were predominantly early region (E1, E2, and E3) junctions, albeit a significant proportion are MLP-derived (__Table 2a__). Junctions from the E2 region were the most abundant at this time point, constituting `r round(most_sig_12, 1)`% of all junctions. The two most abundant junctions at 12 h.p.i were maintained at 24 h.p.i also as the most significantly expressed. However, the MLP-derived junctions were unsurprisingly the most preponderant overall at this time point, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (__Table 2b__). At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions was not only the most abundant overall - accounting for `r round(most_sig_72, 1)`% of all junctions reads - but also contained the most significantly expressed individual junctions (__Table 2c__. Also see __Supplementary Tables 1a-c__; __Figure 4c__). When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was substantially similar to the pattern seen with all the junctions included (__Figure 4d__).  
Furthermore, we analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection. This revealed that, with the exception of one junction (which was a T-G donor-acceptor pair), all splice donor-acceptor pairs in the final transcriptome were the canonical T-A pair.

@@

**Major Late Promoter Region (MLP) transcripts**.
\newpage
## DISCUSSION/CONCLUSIONS
In the original study where the ORFs of THEV were predicted, ORF4 was predicted in the E1 region spanning the Hyd gene. However, later studies predicted and preferred Hyd instead of ORF4; hence, the current prediction map. However, this study shows that while both Hyd and ORF4 may be both expressed, ORF4 is most likely the bona fide gene.
\newpage

@@

### CODE AVAILABILITY    
All the code/scripts written for analysis of the data is available on github (linkXXXXXX)
\newpage

@@

set_flextable_defaults(font.size = 8)
flextable(tab1) %>% theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed", width = 0.95,
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::font(part = "all", fontname = "Avenir") %>%
  flextable::width(., j = ~ Metric, width = 1.5) %>%
  flextable::set_caption("Overview of sequencing results",
              style = "Table Caption") %>%
  flextable::bold(part = "body", j = ~ Metric)

![](results/r/figures/overlay_alltimes.png)
![](results/r/figures/thev_growth_curve.png)
**Figure 2. a) _Per base coverage of sequence reads mapping to THEV genome by time point_**. The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point show remarkable difference in terms of quantities. There is a dramatic increase of mean coverage/depth from `r dep_4` at 4 h.p.i to `r dep_72` at 72 h.p.i, strongly demonstrating an active infection. Unexpectedly, the pileup of reads seems consistently skewed over similar regions of the genome. We could speculate that the temporal gene expression regulation of THEV is different from MAdVs or this could simply mean that the infection was not well synchronized. However, the relative proportions over these similar regions shows some variation over time. **b) _One-step growth of THEV (VAS vaccine strain) in MDTC-RP19 cell line_**. After infecting cells at an MOI of 100 GCN/cell, triplicates of harvested infected cells were quantified with an in-house qPCR assay measuring the total copies of THEV genome. There is no discernible increase in virus titer up 12 h.p.i, after which there is a steady increase in virus titer is measured. The virus titer expands exponentially beginning from 48 h.p.i, increasing by orders of magnitude before reaching a plateau at 120 h.p.i, probably due to high cell death. GCN: genome copy number.

\newpage
![](results/r/figures/thev_spliced_map.png)
![](results/r/figures/thev_patched_timepoints_spliced_map.png)
**Figure 3. a) __Full transcriptome of THEV__**. THEV transcripts assembled from all time points by `StringTie` are unified forming this final transcriptome (splicing map). Transcripts belonging to the same transcription unit (TU) are located in close proximity on the genome and are color coded and labeled in this figure as such. The organization of TUs in the THEV genome is unsurprisingly similar to MAdVs; however, the MAdV genome shows significantly more transcripts. The TUs are color coded: E1 transcripts - red, E2 - black, E3 - dark grey, E4 - green, MLP - blue. Predicted ORFs are also indicated here, colored light grey. **b) __THEV transcripts identified at given time points__**. Transcripts are color coded as explained in **a**.

\newpage

```{r}
#| tab.id: NULL
set_flextable_defaults(font.size = 8)
flextable(sig_72_juncs) %>% theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed", width = 1,
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::font(part = "all", fontname = "Avenir") %>%
  flextable::set_caption("Table 2c: Most abundant splice junctions at 72h.p.i",
              style = "Table Caption") %>%
  flextable::align(align = "center", part = "all") %>%
  flextable::width(., width = 0.7) %>%
  flextable::width(., j = ~ Reads_Percentage, width = 1)
```
\newpage

![](results/r/figures/trxpt_fpkm_percent_abund.png)

![](results/r/figures/region_fpkm_percent_abund.png)
**Figure 4 Changes in splicing and expression profile of THEV over time.** 
**a)** Expression levels of transcripts over time.
**b)** Expression levels of transcripts by region over time.

\newpage
![](results/r/figures/junc_abundances.png)
**c)** Relative abundances of all splice junctions over time. **d)** Relative abundances of junctions in final transcriptome.

```{r region-by-region_e1_figure, fig.height=16, fig.width=18, warning=FALSE}
set_flextable_defaults(font.size = 7)
ft <- flextable(reg_e1_brkdown,
                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
  theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed",
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::set_header_labels(start = "Start", end = "End",
                               splice_site = "Splice Site",
                               strand = "Strand", trxpt_id = "Transcript ID",
                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
  flextable::align(align = "center", part = "all") %>%
  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
                 colwidths = c(1, 4, 1, 4, 1)) %>%
  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
                                                                  width = 1.5)) %>%
  footnote(., i = 2, j = 11, value = as_paragraph(c("Not validated for TRXPT_4")),
           ref_symbols = c("*"), part = "body")

brkdwn_e1_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
  plot_layout(heights = c(2, 0.05, 2)) +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 22, face = "bold"))

@@

```{r region-by-region_e2ANDim_figure, fig.height=16, fig.width=18, warning=FALSE}
set_flextable_defaults(font.size = 7)
ft <- flextable(reg_e2_brkdown,
                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
                             "strand", "region", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
  theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed",
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::set_header_labels(start = "Start", end = "End",
                               splice_site = "Splice Site",
                               strand = "Strand", trxpt_id = "Transcript ID",
                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
  flextable::align(align = "center", part = "all") %>%
  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
                 colwidths = c(1, 4, 2, 4, 1)) %>%
  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
                                                                  width = 1.5)) %>%
  footnote(., i = 9, j = 12, value = as_paragraph(c("Truncated transcript")),
           ref_symbols = c("*"), part = "body")

brkdwn_e2_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
  plot_layout(heights = c(1, 0.05, 2))

@@

set_flextable_defaults(font.size = 7)
ft <- flextable(reg_e4_brkdown,
                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
  theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed",
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::set_header_labels(start = "Start", end = "End",
                               splice_site = "Splice Site",
                               strand = "Strand", trxpt_id = "Transcript ID",
                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
  flextable::align(align = "center", part = "all") %>%
  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
                 colwidths = c(1, 4, 1, 4, 1)) %>%
  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
                                                                  width = 1.5))

brkdwn_e4_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
  plot_layout(heights = c(1, 0.01, 1)) +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 18, face = "bold"))

@@

set_flextable_defaults(font.size = 7)
ft <- flextable(reg_im_brkdown,
                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
  theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed",
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::set_header_labels(start = "Start", end = "End",
                               splice_site = "Splice Site",
                               strand = "Strand", trxpt_id = "Transcript ID",
                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
  flextable::align(align = "center", part = "all") %>%
  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
                 colwidths = c(1, 4, 1, 4, 1)) %>%
  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
                                                                  width = 1.5))

@@

>>>>

**Changes in THEV splicing profile over time**   
AdV gene expression occurs under exquisite temporal control, supervised by designated promoters for each transcription unit (TU). Each promoter typically produce one or few pre-mRNAs that undergo alternative splicing to yield the manifold repertoire of complex transcripts characteristic of AdVs. To evaluate the activity of each promoter over time, Firstly, `Ballgown` - a program for statistical analysis of assembled transcriptomes, was used to estimate and normalize expression levels of all transcripts in Fragments Per Kilobase of transcript per Million mapped reads (FPKM) units over time. Very few unique splice junctions, reads, and transcripts were counted at 4 h.p.i; hence, this time point was excluded in this analysis. This analysis revealed DBP - from the E2 region - to be the most significantly expressed at 12 h.p.i, whereas MLP region transcripts were most abundantly expressed at 24 and 72 h.p.i as expected (__Figure 4a__). Also, our analysis of the FPKM values of transcripts by region showed a similar pattern: the E2 region as the most significantly overexpressed at 12 h.p.i, after which the MLP region assumes predominance (__Figure 4b__).  
Secondly, we estimated relative abundances of all splice junctions for each time point, counting as significantly expressed only those with coverage of at least 1% of the total splice junction reads counted at the given time point. At 12 h.p.i, `r nrow(sig_12_juncs)` junctions meet the 1% threshold, and were predominantly early region (E1, E2, and E3) junctions, albeit a significant proportion are MLP-derived (__Table 2a__). Junctions from the E2 region were the most abundant at this time point, constituting `r round(most_sig_12, 1)`% of all junctions. The two most abundant junctions at 12 h.p.i were maintained at 24 h.p.i also as the most significantly expressed. However, the MLP-derived junctions were unsurprisingly the most preponderant overall at this time point, accounting for `r round(most_sig_24, 1)`% of all the junction reads counted (__Table 2b__). At 72 h.p.i, the trend of increased activity of the MLP continued as expected; at this time, the MLP-derived junctions were not only the most abundant overall - accounting for `r round(most_sig_72, 1)`% of all junctions reads - but also contained the most significantly expressed individual junctions (__Table 2c__. Also see __Supplementary Tables 1a-c__; __Figure 4c__). When we limited this analysis to only junctions in the final transcriptome, the relative abundances of the junctions for each region over time was substantially similar to the pattern seen with all the junctions included (__Figure 4d__).  
Furthermore, we analyzed splice donor and acceptor site nucleotide usage over time to investigate any peculiarities that THEV may show, generally or over the course of the infection. We found that most splice donor-acceptor sequences were unsurprisingly the canonical GU-AG nucleotides.

@@

**Major Late Promoter Region (MLP) transcripts**.
\newpage

## DISCUSSION/CONCLUSIONS   
In the original study where the ORFs of THEV were predicted, ORF4 was predicted in the E1 region spanning the Hyd gene. However, later studies predicted and preferred Hyd instead of ORF4; hence, the current prediction map. However, this study shows that while both Hyd and ORF4 may be both expressed, ORF4 is most likely the bona fide gene.
For fig2a: There is a dramatic increase of mean coverage/depth from `r dep_4` at 4 h.p.i to `r dep_72` at 72 h.p.i, strongly demonstrating an active infection. Unexpectedly, the pileup of reads seems consistently skewed over similar regions of the genome. We could speculate that the temporal gene expression regulation of THEV is different from MAdVs or this could simply mean that the infection was not well synchronized. However, the relative proportions over these similar regions shows some variation over time.
For fig2b: titer reaching a plateau at 120 h.p.i, probably due to high cell death
\newpage

@@

### CODE AVAILABILITY    
All the code/scripts written for analysis of the data is available on github (linkXXXXX)
\newpage

@@

![](results/r/figures/fig_2.png)
**Figure 2: Increasing levels of THEV over time. a) _Per base coverage of sequence reads mapping to THEV genome by time point_**. The pileup of mRNA reads mapping to THEV genome at the base-pair level for each indicated time point. **b) _One-step growth of THEV (VAS vaccine strain) in MDTC-RP19 cell line_**. After infecting cells at an MOI of 100 GCN/cell, triplicates of harvested infected cells were quantified with an in-house qPCR assay measuring the total copies of THEV genome. There is no discernible increase in virus titer up 12 h.p.i, after which there is a steady increase in virus titer is measured. The virus titer expands exponentially beginning from 48 h.p.i, increasing by orders of magnitude before reaching a plateau at 120 h.p.i. GCN: genome copy number.

\newpage
![](results/r/figures/thev_spliced_map.png)
![](results/r/figures/thev_patched_timepoints_spliced_map.png)
**Figure 3. a) __Full transcriptome of THEV__**. THEV transcripts assembled from all time points by `StringTie` are unified forming this final transcriptome (splicing map). Transcripts belonging to the same transcription unit (TU) are located in close proximity on the genome and are color coded and labeled in this figure as such. The organization of TUs in the THEV genome is unsurprisingly similar to MAdVs; however, the MAdV genome shows significantly more transcripts. The TUs are color coded: E1 transcripts - red, E2 - black, E3 - dark grey, E4 - green, MLP - blue. Predicted ORFs are also indicated here, colored light grey. **b) __THEV transcripts identified at given time points__**. Transcripts are color coded as explained in **a**. 
\newpage

![](results/r/figures/figure_4a_d.png)
**Figure 4: Changes in splicing and expression profile of THEV over time.** 
**a)** Expression levels of transcripts over time.**b)** Expression levels of transcripts by region over time.**c)** Relative abundances of all splice junctions over time. **d)** Relative abundances of junctions in transcriptome.
\newpage

```{r region-by-region_e1_figure, fig.height=16, fig.width=18, warning=FALSE}
set_flextable_defaults(font.size = 7)
ft <- flextable(reg_e1_brkdown,
                col_keys = c("trxpt_id", "start", "end", "intron_len", "splice_site",
                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
  theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed",
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::set_header_labels(start = "Start", end = "End",
                               strand = "Strand", trxpt_id = "Transcript ID",
                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
                               splice_site = "Splice Donor-Acceptor",
                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
  flextable::align(align = "center", part = "all") %>%
  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
                 colwidths = c(1, 4, 1, 4, 1)) %>%
  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
                                                                  width = 1.5)) %>%
  footnote(., i = 2, j = 10, value = as_paragraph(c("Not validated for TRXPT_4")),
           ref_symbols = c("*"), part = "body")

brkdwn_e1_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
  plot_layout(heights = c(2, 0.05, 2)) +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 22, face = "bold"))
```

@@

```{r region-by-region_e2andim_figure, fig.height=16, fig.width=18, warning=FALSE}
set_flextable_defaults(font.size = 7)
ft <- flextable(reg_e2_brkdown,
                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
                             "strand", "region", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
  theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed",
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::set_header_labels(start = "Start", end = "End",
                               splice_site = "Splice Donor-Acceptor",
                               strand = "Strand", trxpt_id = "Transcript ID",
                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
  flextable::align(align = "center", part = "all") %>%
  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
                 colwidths = c(1, 4, 2, 4, 1)) %>%
  flextable::vline(j = c(1, 5, 7, 11), border = fp_border_default(color = "grey",
                                                                  width = 1.5)) %>%
  footnote(., i = 6, j = 12, value = as_paragraph(c("Truncated transcript")),
           ref_symbols = c("*"), part = "body")

brkdwn_e2_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
  plot_layout(heights = c(1, 0.05, 1.5))
```

@@

set_flextable_defaults(font.size = 7)
ft <- flextable(reg_e4_brkdown,
                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
  theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed",
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::set_header_labels(start = "Start", end = "End",
                               splice_site = "Splice Donor-Acceptor",
                               strand = "Strand", trxpt_id = "Transcript ID",
                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
  flextable::align(align = "center", part = "all") %>%
  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
                 colwidths = c(1, 4, 1, 4, 1)) %>%
  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
                                                                  width = 1.5))

brkdwn_e4_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
  plot_layout(heights = c(1, 0.01, 1)) +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 18, face = "bold"))
```

@@

set_flextable_defaults(font.size = 7)
ft <- flextable(reg_im_brkdown,
                col_keys = c("trxpt_id", "start", "end", "splice_site", "intron_len",
                             "strand", "4hpi", "12hpi", "24hpi", "72hpi", "status")) %>%
  theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed",
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::set_header_labels(start = "Start", end = "End",
                               splice_site = "Splice Donor-Acceptor",
                               strand = "Strand", trxpt_id = "Transcript ID",
                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
  flextable::align(align = "center", part = "all") %>%
  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
                 colwidths = c(1, 4, 1, 4, 1)) %>%
  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
                                                                  width = 1.5))

@@

```{r region-by-region_mlp_figure, fig.height=16, fig.width=18, warning=FALSE}
set_flextable_defaults(font.size = 7)
ft <- flextable(reg_mlp_brkdown,
                col_keys = c("trxpt_id", "start", "end", "splice_site",
                             "intron_len","strand", "4hpi", "12hpi",
                             "24hpi", "72hpi", "status")) %>%
  theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed",
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::set_header_labels(start = "Start", end = "End",
                               splice_site = "Splice Donor-Acceptor",
                               strand = "Strand", trxpt_id = "Transcript ID",
                               intron_len = "Intron Length", "4hpi" = "4h.p.i",
                               "12hpi" = "12h.p.i", "24hpi" = "24h.p.i",
                               "72hpi" = "72h.p.i", "status" = "Junction Status") %>%
  flextable::align(align = "center", part = "all") %>%
  add_header_row(., values = c("", "Splice Junction", "", "Junction Reads", ""),
                 colwidths = c(1, 4, 1, 4, 1)) %>%
  flextable::vline(j = c(1, 5, 6, 10), border = fp_border_default(color = "grey",
                                                                  width = 1.5)) %>%
  flextable::width(width = 0.3) %>%
  flextable::width(j = 1, width = 1.5)

brkdwn_mlp_trxtps / plot_spacer()/ gen_grob(ft, fit = "auto", scaling = "full") +
  plot_layout(heights = c(1, 0.02, 1.2))
```

**Figure 9: MLP region transcripts. a)**
\newpage

set_flextable_defaults(font.size = 8)
flextable(tab1) %>% theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed", width = 0.95,
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::font(part = "all", fontname = "Avenir") %>%
  flextable::width(., j = ~ Metric, width = 1.5) %>%
  flextable::set_caption("Table 1: Overview of sequencing results",
              style = "Table Caption") %>%
  flextable::bold(part = "body", j = ~ Metric)

```{r}
#| tab.id: NULL
set_flextable_defaults(font.size = 8)
flextable(sig_72_juncs) %>% theme_zebra() %>%
  flextable::set_table_properties(layout = "fixed", width = 1,
                       opts_pdf = list(caption_repeat = F)) %>%
  flextable::font(part = "all", fontname = "Avenir") %>%
  flextable::set_caption("Table 2c: Most abundant splice junctions at 72h.p.i",
              style = "Table Caption") %>%
  flextable::align(align = "center", part = "all") %>%
  flextable::width(., width = 0.7) %>%
  flextable::width(., j = ~ Reads_Percentage, width = 1)
```
